% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Cies Breijs}{June 12, 1982}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:cies.at.kde.dot.nl}{cies\mbox{}@\mbox{}kde.nl}\sbull
\textsmaller{+}31.646469087\sbull
\href{https://github.com/cies}{github.com/cies}\sbull
\href{http://linkedin.com/in/ciesbreijs}{linkedin.com/in/ciesbreijs}
\\
Mathenesserplein 84\sbull
3022\thinspace {\large \sc ld}\sbull
Rotterdam\sbull
The Netherlands

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Entrepeneurial geek with roots in the open source movement. Passionately enabling software-related teams to deliver. Creates/\,structures/\,improves processes. Architects and helps to implement future-proof solutions. Coaches both individuals and groups.}
\\
\\
At the age of seven (1989) Cies wrote his first lines of code in a \acr{LOGO}-like language on an \acr{MSX} (pre-\acr{PC}).  Two years later he attended a conference on an emerging new technology, the Internet, at the Erasmus University from which he would graduate 16 years later (2000) with a degree in Business Computer Science.

After being introduced to the open source movement in 1997, he taught himself a variety of skills including system administration and programming (Bash, Python, Ruby \& \CPP).  By 2002 he got his pet project \acr{KT}urtle ---a zero-entry-barrier programming environment--- included in \acr{KDE}'s \emph{edu} module, and thereby in almost every Linux distribution.

Extensively travelled Europe and Asia after graduating. On return his professional life became a mix of hands-on work in startups and web software agencies, while settling as a husband and father in personal life.
\end{multicols}


\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection
  {\href{http://cies.breijs.com}{\acr{CIES.BREIJS.COM.}}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Freelance \acr{IT} Consultant}
    {Oct \apo16 -- present}
    {\bodytext{Provides services related to software development, such as:\@ coaching, audits, process improvement, web/cloud architecture, recruitment strategy and tender advise.  Clients:\@ \href{http://www.burst-digital.com/en}{Burst}, \href{https://hoppinger.com}{Hoppiner} \& \href{http://bit4u.nl}{Bit4U}.}}
}

\headedsection
  {\href{http://www.hoppinger.com}{Hoppinger}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Head of Technology}
    {Apr \apo12 -- Oct \apo16}
    {\bodytext{Hoppinger is an open source minded \emph{full-service} internet agency.  In charge of the dev't capacity, reporting directly to managing director and co-founder Marijn Bom.  Drafted and carried out the technical company vision.  Inspired both devs and management to look beyond \acr{PHP}. Grew custom app dev't into a serious revenue segment.  Implemented continuous delivery. Created and taught several in-house courses.  Enacted testing strategy.  Recruited viciously, in part by organizing educational events.  Restructured to fixed team configurations.  Introduced DevOps (Puppet).  Helped to set up the \textit{Customer Support} and \textit{IT ops} dep'ts.  Contributed to the sales pitches for, and in charge of the software architecture for, all technically challenging projects. Involved with many company-wide process improvements.}}
}

\headedsection
  {\href{http://www.hr.nl}{Rotterdam University of Applied Sciences}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Member of the Professional Advisory Board \textnormal{\textit{(till Sep \apo16)}} \& Guest Lecturer}
    {Sep \apo12 -- present}
    {%\bodytext{Introductory lecture on history of software development and open source for 1\textsuperscript{st} year CS students.}
    }
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://www.intellecap.com}{Intellecap}/\href{http://istpl.in}{\acr{ISTPL}}}
  {\textsc{Mumbai, Pune \& Hyderabad, India}} {%

  \headedsubsection  % sets the header for a subsection and contains usually body text
    {\acr{IT} Consultant}
    {Nov \apo08 -- Feb \apo09}
    {\bodytext{Intellecap is a financial advisory firm serving corporates, non-profits and governments working in developing markets. Assessed their software development team and processes. Trained their devs. Architected and built several web apps; one being Mostfit an open source \acr{MIS} for \href{http://en.wikipedia.org/wiki/Microcredit}{microcredit} lenders.}}

  \headedsubsection
    {\acr{IT} \& Strategy Consultant}
    {Jan \apo10 -- Aug \apo11}
    {\bodytext{Called in to solve several technical challenges and develop growth strategies regarding Mostfit.}}

  \headedsubsection
    {CTO}
    {Oct \apo11 -- Feb \apo12}
    {\bodytext{Proudly joined the \acr{C}-family of Intellicap's software division, ISTPL, to make \href{https://github.com/Mostfit/mostfit}{Mostfit} the nr.1 software solution for micro credit lenders around the globe.  Shut down in six months due to lack of investment.}}
}

\headedsection
  {\href{http://www.zarafa.com}{Zarafa}}
  {\textsc{Delft, The Netherlands}} {%
  \headedsubsection
    {\acr{QA} \& Release Manager}
    {Dec \apo09 -- Jan \apo11}
    {\bodytext{Before 2015, when Zarafa entered in an extensive parnership with Amazon, it was probably the fastest growing open source product company in Europe, making a drop-in replacement for MS Exchange.  Reported directly to the \acr{CEO}, Brian Josef, and worked closely with the \acr{CTO}, Steve Hardy.  In charge of the 6 men strong QA dep't.  Established test automation and continuous integration.  Architected and implemented an all-integrated documentation and translation system that employed community effort.  Got sent to India to analyse and streamline their outsourced operations.}}
}

\headedsection
  {\href{http://www.dharmapublishing.com}{Dharma Publishing}}
  {\textsc{near San Francisco, \acr{USA}}} {%
  \headedsubsection
    {\acr{IT} Consultant}
    {Nov \apo09 -- Dec \apo09}
    {\bodytext{Dharma Publishing, the worlds largest Buddhist publisher, is a non-profit, all-volunteer organisation to preserve Tibetan buddhism and culture. Built their web shop, improved related processes.}}
}

\headedsection
  {\href{http://www.kde.org}{KDE}}
  {\href{http://edu.kde.org/kturtle}{edu.kde.org/kturtle}} {%
  \headedsubsection
    {Software Engineer}
    {Dec \apo03 -- present}
    {\bodytext{\acr{KT}urtle is an educational programming environment that simplifies learning the basics of programming.  \acr{KT}urtle is intended as a gift to future generations:\ a simple environment to get started with programming.  In 2003 \acr{KT}urtle got admitted to the \acr{KDE} project.}}
}

\headedsection
  {\href{http://truetopiaproject.org}{Truetopia Project}}
  {\href{http://truetopiaproject.org}{truetopiaproject.org}} {%
  \headedsubsection
    {Initiator \& Lead Developer}
    {Nov \apo07 -- Apr \apo10}
    {\bodytext{The Truetopia Project is an open source web application (Rails) to facilitate self-governing communities.  It provides a workflow for collaborative problem identification and solution design.}}
}

\headedsection
  {\href{http://www.dpu.ac.th/dpuic}{Dhurakij Pundit University International College}}
  {\textsc{Bangkok, Thailand}} {%
  \headedsubsection
    {Guest Lecturer}
    {Sep \apo09}
    {\bodytext{Invited by Dr.\@ Pilun Piyasirivej and Mr.\@ Michel Bauwens to deliver several guest lectures.}}
}

\headedsection
  {\href{http://www.opendream.th}{Opendream}}
  {\textsc{Bangkok, Thailand}} {%
  \headedsubsection
    {Freelance \acr{IT} Consultant}
    {Aug \apo09 -- Sep \apo09}
    {\bodytext{Architected and largely implemented an open source media sharing web service (\acr{REST API}) that facilitates video uploads, transcoding and streaming.  Coached their development team on system design, Ruby web development and software engineering methodologies (Scrum/\acr{TDD}/\acr{BDD}).}}
}

\headedsection
  {\href{http://www.commuun.nl}{Commuun}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Senior Visionary}
    {Jul \apo06 -- Sep \apo09}
    {\bodytext{Set up the technical infrastructure, defined the business cases, created the brand and built several Rails-based web applications with Peter Duijnstee, my close friend and proprietor of Commuun.}}
}

\headedsection
  {\href{http://www.eur.nl}{Erasmus University Rotterdam}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Guest Lecturer}
    {Jul \apo06 -- Jul \apo09}
    {\bodytext{Spoke on the phenomenon of open source on request of Prof.\ Michiel van Wezel.}}
}

%\headedsection
%  {LIP Automatisering}
%  {\textsc{Breda, The Netherlands}} {%
%  \headedsubsection
%    {Software Auditor}
%    {Sep \apo06}
%    {\bodytext{Audited their flag ship product \emph{\acr{LIP} Suite}:\ an %\acr{ERP} solution for construction companies.}}
%}

\headedsection
  {
    \href{http://www.thehealthagency.com}{The Health Agency}
    \acr{(now \href{http://www.minddistrict.com}{MindDistrict})}
  }
  {\textsc{Delft \& Rotterdam, The Netherlands}} {%

  \headedsubsection
    {Software Engineer}
    {Jun \apo05 -- Feb \apo06}
    {\bodytext{Worked on their \acr{CMS} (written in Python and uses Postgre\acr{SQL}, \acr{XML}/\acr{XSLT} and Twisted).}}

  \headedsubsection
    {Software Auditor}
    {Dec \apo06}
    {\bodytext{Assessed their Python/Zope/\acr{Z}o\acr{DB}-based product re-engineering effort.}}
}

\vspace{-0.2em}
\begin{center}
  \emph{\small Please refer to \href{http://www.linkedin.com/in/ciesbreijs}{Cies' LinkedIn profile} for a more complete list of work experience along with recommendations.}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{http://www.eur.nl/english}{Erasmus University Rotterdam}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {BSc in Business Computer Science \textnormal{~(\acr{CS}~\,\&\,Economics)}}
    {2004 -- 2007}
    {\bodytext{Main projects on the economics of open source and the semantic web (\acr{RDF}/\acr{RDFS}, \acr{OWL} \& \acr{SPARQL}).}}
}

\headedsection
  {\href{http://www.tudelft.nl/en}{Technical University Delft}}
  {\textsc{Delft, The Netherlands}} {%
  \headedsubsection
    {Industrial Design Engineering \textnormal{\textit{~(discontinued)}}}
    {2001 -- 2002} {}
}

\headedsection
  {\href{http://www.libanonlyceum.nl}{Libanon Lyceum}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {VWO \textnormal{~(Pre-University Secondary Education)}}
    {1994 -- 2000} {}
}


\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Leading and recruiting teams of software engineers.  Big fan of Agile methodologies, continuous delivery and functional programming.  Enjoys writing Ruby/\nsp Python/\nsp Java/\nsp \CPP~and Haskell.  Solid knowledge of the full web technology stack.  Able to architect \textit{and} implement distributed/\acr{HA} systems.  Strong Linux administration skills (e.g.\ Bash scripting, Apache/\acr{NGINX}, Postgres/My/No\acr{SQL}, ElasticSearch).  Well experienced with virtualization/containerization (Docker/Kubernetes, \acr{KVM}, Xen and several \acr{AWS} solutions) and DevOps (Puppet).  Emacs user.}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {Dutch \emph{(mother tongue)}, English \emph{(full professional proficiency)}, German \emph{(limited working proficiency)}, French \emph{(elementary proficiency)} and Mandarin Chinese \emph{(beginner)}.}


\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {art, Buddhism, cryptography, functional programming, Go (board game), history, music (from classical and jazz to Berlin-techno), \acr{NLP}, permaculture, philosophy, rock climbing, startups, travel, typography (e.g.\ graphic design, \LaTeX), \acr{UX}-design and vegan cuisine.}


\end{document}

